---
title: "documenter"
author: "Zachary Colburn"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Overview
It is sometimes necessary to document all the files in a directory. Using the function *document_it*, all files can quickly and thoroughly be aggregated automatically into a double spaced document. By creating an annotation file, additional comments can be added for each file without additional intervention.


# Usage
The package can be loaded via the *library* function.
```r
# Load the package.
library(documenter)
```


The function *document_it* accepts 3 arguments:


- *input_directory*: The directory of files to be documented.
- *output_file*: The path to the output file that will be generated.
- *annotation_file*: The path to the annotation file if present.


An example use case is provided below. This documents all files in the "example" folder within the documenter package directory. Note that this is a recursive operation. Thus, all files contained within subdirectories of the folder will also be documented. Note that the output generated by this example is written to a folder in the temporary directory.
```{r eval=FALSE}
input <- system.file("extdata", "example", package = "documenter")
document_it(
  input_directory = input,
  output_file = file.path(tempdir(), "documentation"),
  annotation_file = NULL
)
```


## Disclaimer
The views expressed are those of the author(s) and do not reflect the official policy of the Department of the Army, the Department of Defense or the U.S. Government.